INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION

### 2016-09-13 paper.tex
Add experiment description and table

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION}
%
% Single address.
% ---------------
%\name{Dmitriy Serdyuk $^{\dagger}$ \qquad Kartik Audhkhasi$^{\star}$ \and Philemon Brakel$^{\dagger}$ \and Bhuvana Ramabhadran$^{\star}$  \and Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
%\address{$^{\dagger}$ Universit\'e de Montr\'eal, $^{\star}$ IBM}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Phil\'emon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
  {$^{\dagger}$ Universit\'e de Montr\'eal \\
  $^{\star}$ IBM}
  {}
  {}

@@

    This work focuses on investigation of neural architectures which produce
    representations invariant to certain conditions as the noise type for speech
    recognition. Similar
    to the Ganin et al. work we train the intermediate representation to be invariant
    to noise conditions training three neural networks: the encoder, the recognizer, and the
    noise classifier to produce the representation produced by the encoder to decrease
    the performance of the classifier making the representation invariant to noise conditions. We
    experimentally evaluate proposed architectures on the acoustic modelling task
    for speech recognition on a popular benchmark Aurora4.
\end{abstract}
%
\begin{keywords}
speech recognition, deep neural networks, invariant representations, adversarial training
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
    One of the most challenging aspects of automatic speech recognition (ASR),
    is the mismatch between the training and testing conditions. During
    testing, a system may encounter new recording conditions, microphone types,
    accents and types of background noises. Even if all testing conditions also appeared
    in the train data, their relative distribution is likely to be
    different. For this reason, it's important to develop systems that are
    robust towards changes in recording conditions in general.

@@

\section{Experiments}
We experimentally evaluate the approach discussed in Section~\ref{sec:gradient-reverse} 
on a noisy speech recognition dataset Aurora-4~\cite{parihar2002aurora}. This dataset
is based on the Wall Street Journal (WSJ0 is available at LDC). Additive noise of 
six categories (airport, babble, car, restaurant, street, train) was introduced to the 
clean data. We used mel-filterbank features with their deltas and delta-deltas spliced
over 5 frames on each side making 11 consecutive frames and 1320 input features. 
We did not use any speaker normalization of input features. We pretrained 5 layer
speech recognition network with 2048 rectified linear units at every layer using Adam 
optimization algorithm for 5 epochs. After pretraining, we turned on the invariance term.

First expriment we performed is the gender invariance. We added a 2 layer network 
branching off the last layer of the pretrained speech recognition network and 
trained it until convergence with SGD. Although, the performance remained unchanged,
the t-SNE visualization on Figure~\ref{fig:tsne} demonstrates that the hidden units
are less separated in the projected space.

\begin{figure}
    \centering
    %TODO: add image
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=\linewidth]{tsne-original.png}
    \end{subfigure}%
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=\linewidth]{tsne-invariant.png}
    \end{subfigure}%
    \caption{t-SNE visualization of the last hidden layer. On the left, the baseline
    model. On the right, the model trained with the adversarial objective. Colors 
    represent genders.}
    \label{fig:tsne}
\end{figure}

>>>>

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION}
%
% Single address.
% ---------------
\name{Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Phil\'emon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
\address{$^{\dagger}$ Universit\'e de Montr\'eal\\
         $^{\star}$ IBM}

@@

    This work focuses on investigation of neural architectures which produce
    representations invariant to certain conditions as the noise type for speech
    recognition. Similar
    to the Ganin et al. work we train the intermediate representation to be invariant
    to noise conditions training three neural networks: the encoder, the recognizer, and the
    noise classifier to produce the representation produced by the encoder to decrease
    the performance of the classifier making the representation invariant to noise conditions. We
    experimentally evaluate proposed architectures on the acoustic modelling task
    for speech recognition on a popular benchmark Aurora-4.
\end{abstract}
%
\begin{keywords}
speech recognition, deep neural networks, invariant representations, adversarial training
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
    One of the most challenging aspects of automatic speech recognition (ASR),
    is the mismatch between the training and testing conditions. During
    testing, a system may encounter new recording conditions, microphone types,
    accents and types of background noises. Even if all testing conditions also appeared
    in the train data, their relative distribution is likely to be
    different. For this reason, it's important to develop systems that are
    robust towards changes in recording conditions in general.

@@

\section{Experiments}
We experimentally evaluate the approach discussed in Section~\ref{sec:gradient-reverse} 
on a noisy speech recognition dataset Aurora-4~\cite{parihar2002aurora}. This dataset
is based on the Wall Street Journal corpus (WSJ0 is available at LDC). Additive noise of 
six categories (airport, babble, car, restaurant, street, train) was introduced to the 
clean data. We used mel-filterbank features with their deltas and delta-deltas spliced
over 5 frames on each side making 11 consecutive frames and 1320 input features in total. 
We did not use any speaker normalization of input features. We pretrained 5 layer
speech recognition network with 2048 rectified linear units at every layer using Adam 
optimization algorithm for 5 epochs. After pretraining, we turned on the invariance term.

The first expriment we performed is the gender invariance. We added a 2 layer network 
branching off the last layer of the pretrained speech recognition network and 
trained it until convergence with SGD. Although, the performance remained unchanged,
the t-SNE visualization in Figure~\ref{fig:tsne} demonstrates that the hidden units
are less separated in the projected space.

Next, we trained a model for the noise condition invariance. We used an architecture
similar to one described above with a binary invariance classifier target denoting 
whether the utterance is clean or noisy. We oversampled the noisy utterances to 
address the fact that the labels are not ballanced, the clean subset has approximately 4400
when every noisy condition subset contains only 443 utterances. The results are
summarized in Table~\ref{tab:results}.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=\linewidth]{tsne-original.png}
    \end{subfigure}%
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=\linewidth]{tsne-invariant.png}
    \end{subfigure}%
    \caption{t-SNE visualization of the last hidden layer using the clean development
    subset. On the left, the baseline
    model. On the right, the model trained with the adversarial objective. Colors 
    represent genders.}
    \label{fig:tsne}
\end{figure}

\begin{table}
    \centering
    \caption{Results for word error rate (WER\%) on Aurora-4 dataset.}
    \label{tab:results}
    \begin{tabular}{r|cc|cc}
    \multirow{2}{*}{Subset} & \multicolumn{2}{c}{Orig}  & \multicolumn{2}{|c}{Inv}\\ 
               & wv1  & wv2  & wv1  & wv2 \\
    \hline 
    clean      & 4.04 & 6.76 & & \\
    airport    & 7.44 & 15.36& & \\
    babble     & 7.86 & 15.88& & \\
    car        & 4.17 & 8.99 & & \\
    restaurant & 9.25 & 17.32& & \\
    street     & 7.79 & 16.14& & \\
    train      & 8.18 & 17.26& & \\
    \hline
    Average    & \multicolumn{2}{c}{10.46}& & 
    \end{tabular}
    %TODO: add numbers!
\end{table}
